Final_Project_Work_HW2_JaJuArEm

### 2022-09-29 Final_Project_Work_HW2.Rmd
Newest version 9/28/2022

# creation of cv folds
# model spec
# recipes & workflows
# fit & tune models

>>>>

# creation of cv folds

```{r}
data_cv10 <- vfold_cv(imdb_clean, v = 10)
```

# model spec

```{r}
lm_spec <-
    linear_reg() %>% 
    set_engine(engine = 'lm') %>% 
    set_mode('regression')
```

# recipes & workflows

```{r}
full_rec <- recipe(Gross ~ ., data = imdb_clean) %>%
    step_rm(Series_Title, Released_Year, Overview) %>% 
    step_nzv(all_predictors()) %>% 
    step_normalize(all_numeric_predictors()) %>% 
    step_dummy(all_nominal_predictors())

full_lm_wf <- workflow() %>%
    add_recipe(full_rec) %>%
    add_model(lm_spec)

full_model <- fit(full_lm_wf, data = imdb_clean)

full_model %>% tidy()
```

# fit & tune models

```{r}
